State of the Practice for Medical Imaging Software

### 2021-12-11 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Minor updates to MI SOP paper
Answer questions to MI paper

Although teams may have a process for accepting new contributions, no one
discussed this during their interview. However, most teams (8 of 9) mentioned
using GitHub and pull requests to manage contributions from the community. The
interviewees generally gave very positive feedback on using GitHub. Some teams
previously used a different approach to version control and eventually
transferred to git and GitHub.  The past approaches included contributions
from e-mail (3 teams), contributions from forums (1 team) and sharing the
git repository via e-mail (1 team).  \wss{I do not know what this last one means.
Should ask Ao.}

@@

The interviewees identified multiple threats to correctness.  The most
frequently mentioned threat was complexity.  Complexity enters the software by
various means, including a variety of data formats, complicated data standards,
differing outputs between medical imaging machines, and the addition of
(non-viewing related) functionality.  Other threats to correctness identified by at least one time
include the following:
\begin{itemize}
\item Lack of real world image data for testing;
\item The team cannot use private data for debugging even when the data causes
problems; \wss{Why not?  Should ask Ao}
\item Expense and time consumed by tests because of the huge datasets;
\item Difficulty managing releases;
\item No unit tests; and,
\item No dedicated quality assurance team.
\end{itemize}

@@

The discussion with the developers focused on understandability issues for two
classes of users: the end users and other developers.  The threats to
understandability for end users include users not understanding how to use
features (\wss{Because the users don't have sufficient background?  Ask Ao.}),
the team not having a dedicated user experience (UX) designer, some important
indicators are not noticeable (e.g. a progress bar), not all users understand
the purpose of the software, not all users know if the software includes certain
features, not all users understand how to use the command line tool, not all
users understand that the software is a web application. For developers the
threats to understandability include developers not understanding how to deploy
the software (\wss{This sounds like a consequence of a lack of
understandability, rather than threat to it.  Or is the point that developers
lack sufficient background?  Ask Ao}), and the architecture is difficult for new
developers to understand.

@@

We discussed threats to reproducibility and strategies for improving it.  The
threats that were mentioned include closed-source software, no user interaction
tests, no unit tests, using different versions of some common libraries
\wss{because the interface and/or behaviour of the library could have changed?
Ask Ao}, variability between CPUs, and misinterpretation of how manufacturers
create medical images. The most commonly cited (by 6 teams) strategy to improve
reproducibility was testing (regression tests, unit tests, having good tests).
The second most common strategy (mentioned by 5 teams) is making code, data, and
documentation available, possibly by creating open-source libraries.  Other
ideas that were mentioned include running the same tests on all platforms, a
dockerized version of the software to insulate it from the OS environment, using
standard libraries, monitoring the upgrades of the library dependencies, clearly
documenting the version information, bringing along the exact versions of all
the dependencies with the software, providing checksums of the data, and
benchmarking the software against other software that overlaps in functionality.
Specifically one interviewee suggested using \textit{3D Slicer} as the benchmark
to test their reproducibility.

@@

We identified the use of unit testing in less than half of the 29 projects. On
the other hand, the interviewees believed that testing (including usability
tests with users) was the top solution to improve correctness, usability, and
reproducibility. One pain point in the development process is the lack of access
to real-world datasets for testing. The developers' strategies to address this
are summarized in Section~\ref{sec_pain_points_3}. One threat to correctness is:
with huge datasets for testing, the tests are expensive and time-consuming.
Three interviewees endorsed self tests / automated tests, which may save time
for testing.

@@

- add more on comparison to existing literature surveys
- ask Mike:
    - for journal version ask for more figures?

>>>>

Although teams may have a process for accepting new contributions, no one
discussed this during their interview. However, most teams (8 of 9) mentioned
using GitHub and pull requests to manage contributions from the community. The
interviewees generally gave very positive feedback on using GitHub. Some teams
previously used a different approach to version control and eventually
transferred to git and GitHub.  The past approaches included contributions
from e-mail (3 teams), contributions from forums (1 team) and sharing the
git repository via e-mail (1 team).  \wss{I do not know what this last one means.
Should ask Ao.} \ad{The last one happened when cloud-based repositories (Github,
Gitlab, Bitbucket, etc.) were not widely used. The project git repository was
stored locally on the project owner's local computer. The owner shared the whole
git repo to team members and other individuals who wanted to contribute. The
contributors made changes to the repo, and sent it back. They transferred the
repo back and forth by email.}

@@

The interviewees identified multiple threats to correctness.  The most
frequently mentioned threat was complexity.  Complexity enters the software by
various means, including a variety of data formats, complicated data standards,
differing outputs between medical imaging machines, and the addition of
(non-viewing related) functionality.  Other threats to correctness identified by at least one time
include the following:
\begin{itemize}
\item Lack of real world image data for testing;
\item The team cannot use private data for debugging even when the data causes
problems; \wss{Why not?  Should ask Ao} \ad{For example, when a physician faces
some problems to use the software to display a medical image, he/she might reach
to the team for help. However, the image is private, so the physician can only
describe the problems, but not share the image with the team to reproduce the
problems for debugging.}
\item Expense and time consumed by tests because of the huge datasets;
\item Difficulty managing releases;
\item No unit tests; and,
\item No dedicated quality assurance team.
\end{itemize}

@@

The discussion with the developers focused on understandability issues for two
classes of users: the end users and other developers.  The threats to
understandability for end users include users not understanding how to use
features (\wss{Because the users don't have sufficient background?  Ask Ao.})
\ad{Did you mean medical or medical imaging background? No, it was majorly
caused by the software usability. Based on the context of our interview
conversations, it means that users don't understand how to complete certain
operations or what functions a feature provides. It's due to unclear description,
lack of documentation, poorly designed UI or nonintuitive process},
the team not having a dedicated user experience (UX) designer, some important
indicators are not noticeable (e.g. a progress bar), not all users understand
the purpose of the software, not all users know if the software includes certain
features, not all users understand how to use the command line tool, not all
users understand that the software is a web application. For developers the
threats to understandability include developers not understanding how to deploy
the software (\wss{This sounds like a consequence of a lack of
understandability, rather than threat to it.  Or is the point that developers
lack sufficient background?  Ask Ao}) \ad{Yes, this should be a consequence of a
lack of understandability. I think the direct cause is that the project doesn't
clearly explain how to deploy. The background of the developers wasn't discussed
at that point.}, and the architecture is difficult for new
developers to understand.

@@

We discussed threats to reproducibility and strategies for improving it.  The
threats that were mentioned include closed-source software, no user interaction
tests, no unit tests, using different versions of some common libraries
\wss{because the interface and/or behaviour of the library could have changed?
Ask Ao} \ad{Yes. Behaviour change could be caused by a lib changing to use
different algorithms or different dependencies}, variability
between CPUs, and misinterpretation of how manufacturers
create medical images. The most commonly cited (by 6 teams) strategy to improve
reproducibility was testing (regression tests, unit tests, having good tests).
The second most common strategy (mentioned by 5 teams) is making code, data, and
documentation available, possibly by creating open-source libraries.  Other
ideas that were mentioned include running the same tests on all platforms, a
dockerized version of the software to insulate it from the OS environment, using
standard libraries, monitoring the upgrades of the library dependencies, clearly
documenting the version information, bringing along the exact versions of all
the dependencies with the software, providing checksums of the data, and
benchmarking the software against other software that overlaps in functionality.
Specifically one interviewee suggested using \textit{3D Slicer} as the benchmark
to test their reproducibility.

@@

We identified the use of unit testing in less than half of the 29 projects. On
the other hand, the interviewees believed that testing (including usability
tests with users) was the top solution to improve correctness, usability, and
reproducibility. One pain point in the development process is the lack of access
to real-world datasets for testing. The developers' strategies to address this
are summarized in Section~\ref{sec_pain_points_3} \ad{to be fixed}. One threat to correctness is:
with huge datasets for testing, the tests are expensive and time-consuming.
Three interviewees endorsed self tests / automated tests, which may save time
for testing.

@@

- add more on comparison to existing literature surveys
- ask Mike:
    - for journal version ask for more figures?
    - for journal double blind solution
    - can he submit
    - potential reviewers
    - feedback
- Radiology - should not exceed 6000 words, 50 refs, 8 figures and 4 tables
